DeepAutoTrack (DAC): Car Trajectory Prediction for Autonomous Driving

### 2017-11-13 paper/cvpr2018/cvpr2018_draft.tex

\newcommand{\argmin}{\operatornamewithlimits{argmin}}
%\cvprfinalcopy

@@

\author{Di Wu, Zhennan Wang, Yi Tang,  Wenbin Zou, Xia Li\\
Shenzhen University\thanks{Shenzhen Key Lab of Advanced Telecommunication and Information Processing, College of Information Engineering, Shenzhen University.}\\
{\tt\small dwu,...@szu.edu.cn}}
\maketitle
%%%%%%%%% ABSTRACT
\begin{abstract}
% State the problem, your approach and solution, and the main contributions of the paper. Include little if any background and motivation. Be factual but comprehensive. The material in the abstract should not be repeated later word for word in the paper.

Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
These models need to be temporally consistent and visually interpretable.
Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
In this paper, we raise the question of ``can we predict car's future odometry given previous egomotion visual input?".
The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
Then, a novel DRN-LSTM network is incorporated to fuse the multiple-streams from past frames to predict targets' future trajectories.
We demonstrate the feasibility of predicting future trajectories of cars for assisting mediated perception.
 We also show the effectiveness of using privileged information (e.g., scene semantics and car pose information) further boost the prediction accuracy across diverse traffic conditions.

\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {\small TODO: Pull figure caption goes here.}}
        \label{fig:pull_figure}
\end{figure}
\textbf{\emph{3. Why is it hard? (E.g. why do naive approaches fail?)}}

@@

In traditional vision based tracking problems(\emph{e.g.} ~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement of the target in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
However, traffic participants generally exhibit regular trajectories (e.g., cars driving on the road and pedestrian walking on the sidewalks).

@@

TODO: TY
%%% DW: write related work for visual tracking
%%% DW: write related dataset for autonoumous driving

@@

TODO: DW
%% DW: (1)traditional segmentic segmentation dataset
%% DW: (2) synthetic dataset
%% DW: (3) temporal consistent dataset

@@

TODO: cite below papers;
~\cite{xu2017end}: End-to-end learning of driving models from large-scale video dataset.

@@

\subsubsection{Traffic participants detection}

@@

\begin{table*}\centering
\ra{1.}
\begin{tabular}{@{}llllllllllll@{}}\toprule
\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
\hline
\multirow{3}{*}{SSD}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
                    &    recall   & \textbf{92.3}  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
                    &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
\multirow{3}{*}{Faster-RCNN}
                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
\bottomrule
\end{tabular}
\caption{Caption: TODO results: (1) SSD better at detecting large object(which is in our case). (2) Faster-RCNN  is more robust to confidence threshold}
\label{tab:ssd_fasterrcnn}
\end{table*}

>>>>

\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\cvprfinalcopy

@@

\author{Di Wu, Zhennan Wang, Yi Tang,  Wenbin Zou, Xia Li\\
Shenzhen University\thanks{Shenzhen Key Lab of Advanced Telecommunication and Information Processing, College of Information Engineering, Shenzhen University.}\\
{\tt\small dwu,...@szu.edu.cn}}
\maketitle
%%%%%%%%% ABSTRACT
\begin{abstract}
TODO: abstract
This guide is patterned after my “Doing well in your courses”, a post I wrote a long time ago on some of the tips/tricks I’ve developed during my undergrad. I’ve received nice comments about that guide, so in the same spirit, now that my PhD has come to an end I wanted to compile a similar retrospective document in hopes that it might be helpful to some. Unlike the undergraduate guide, this one was much more difficult to write because there is significantly more variation in how one can traverse the PhD experience. Therefore, many things are likely contentious and a good fraction will be specific to what I’m familiar with (Computer Science / Machine Learning / Computer Vision research). But disclaimers are boring, lets get to it!
\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}

\begin{figure}

\includegraphics[width=8.8cm]{pool_figure}
\caption{pool figure}
\label{figure10}
\end{figure}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {\small TODO: Pull figure caption goes here.}}
        \label{fig:pull_figure}
\end{figure}
\textbf{\emph{3. Why is it hard? (E.g., why do naive approaches fail?)}}

@@

In traditional vision based tracking problems (\emph{e.g.} ~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement of the target in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
However, traffic participants generally exhibit regular trajectories (e.g., cars driving on the road and pedestrian walking on the sidewalks).

@@

TODO: TY
%%% DW: write related work for visual tracking
%%% DW: write related dataset for autonoumous driving
Object detection is an important component in our system. Before the resurgence of convolutional neural network (CNN), Deformable Part Model (DPM) \cite{felzenszwalb2008discriminatively} and Selective Search \cite{Uijlings2013Selective} are the trend of this field. However, after the proposal of R-CNN \cite{girshick2014rich}, which combines Selective Search and deep learning features to detect objects, the architecture of CNN has attracted more attention. At the beginning, R-CNN is a step-by-step and inefficient method. Then, SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features and Fast R-CNN \cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network. At last, Faster R-CNN \cite{Ren2015Faster} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build a end-to-end architecture. Meanwhile, SSD \cite{liu2016ssd} uses a series of boxes and directly gives the probability for each object class. In addition, YOLO \cite{redmon2016you} proposes a fast object detection method, which divides the input image into grids, then predicts object positions and confidences for each category in each grid.

At the field of semantic segmentation, many methods with CNN also bring a dramatic improvement. FCN \cite{long2015fully} firstly transfers the fully-connected layers into convolution layers, which turns segmentation task into pixel-wise classification task. Deeplab \cite{chen2016deeplab} considers the limitation of receptive field of CNN, and then proposes a dilated convolution layer to solve this problem. DRN \cite{yu2017dilated} further proposes a semantic network by integrating residual structure and dilated convolution. With the modification of neural network, conditional random field (CRF) is employed into refining the output of network in \cite{chen2016deeplab}. After that, CRF is merged into neural network to become an end-to-end architecture \cite{liu2015semantic,zheng2015conditional,arnab2016higher}

@@

TODO: DW

%% DW: (1)traditional segmentic segmentation dataset
%% DW: (2) synthetic dataset
%% DW: (3) temporal consistent dataset

@@

TODO: cite below papers;

~\cite{xu2017end}: End-to-end learning of driving models from large-scale video dataset.

@@

\begin{table*}\centering
\ra{1.}
\begin{tabular}{@{}llllllllllll@{}}\toprule
\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
\hline
\multirow{3}{*}{SSD}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
                    &    recall   & \textbf{92.3}  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
                    &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
\multirow{3}{*}{Faster-RCNN}
                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
\bottomrule
\end{tabular}
\caption{Caption: TODO results: (1) SSD better at detecting large object(which is in our case). (2) Faster-RCNN  is more robust to confidence threshold}
\label{tab:ssd_fasterrcnn}
\end{table*}
\subsubsection{Traffic participants detection}

@@
